\added{GrapeCPNet: A Self-supervised Point Cloud Completion Network for 3D Phenotyping of Grape Bunches}

### 2025-04-30 main.v0.edits.tex
rm v0 changes

\textbf{\added{Highlights}}

\begin{itemize}
%   \item Novel deep learning pipeline for automated 3D grape phenotyping.
%   \item GrapeCPNet: Self-supervised network for berry points cloud completion.
%   \item High accuracy in berry instance segmentation (99.5\% average precision).
%   \item Robust performance across four grape varieties ($R^2$ of 0.855 for radius, 0.969 for 
% volume).
%   \item Non-destructive and high-throughput analysis for viticulture applications.
  \item \added{GrapeCPNet completes 3D point clouds for segmented berry instances.}
  \item \added{GrapeCPNet is trained using self-supervision, free of manual annotations.}
  \item \added{Integrated into a deep learning pipeline for automated 3D grape bunch phenotyping.}
  \item \added{Achieved over 0.85 $R^2$ and 99.5\% average precision on four grape varieties.}
\end{itemize}

@@

\added{Another challenge after the success of instance berry segmentation is the incomplete representation of berry surfaces.} 
The aggregated cluster growth causes the berries to squeezed against each other, leading to self occlusion and resulting in an incomplete point cloud of berry surfaces \citep{du_instance_2023}. 
Therefore, point cloud instance segmentation can only capture partial information rather than that of whole berries.
To address \replaced{this issue}{the issue of partial point clouds,} and consequently an underestimation of the berry traits, point cloud shape completion is one of the most commonly used solutions.
Point cloud completion is the task of generating a complete 3D shape given partial point cloud input \citep{tesema_point_2024}. 
For instance, \citet{ge_symmetrybased_2020} assume that strawberries are symmetrical, suggesting that their shape can be completed by mirroring the existing shape, provided an appropriate symmetrical plane can be identified.
\citet{marangoz_fruit_2022} proposed an super-ellipsoids matching approach to map fruits on plants and estimate their shape.
However, these methods are limited to specific fruit characteristics and require manual design of algorithms according to the features of the fruit, lacking the potential for generalized application.
Utilizing deep learning methods, researchers have designed point cloud completion networks \citep{wang_unsupervised_2021}. 
\citet{park_deepsdf_2019} introduced DeepSDF to achieve the completion of object point cloud models. It uses a learned continuous signed distance function to represent a class of shapes in latent space and is tolerant to noisy 3D input data. 
\citet{magistri_contrastive_2022} utilized DeepSDF and its latent space in an encoder-decoder network that converted a single RGB-D frame to a 3D shape of a complete fruit. 
This encoder-decoder network was extended and optimized by \citet{blok_highthroughput_2025} for high-throughput 3D shape completion of potato tubers on a commercial harvester. 
\deleted{Outside the agricultural domain, tang\_lakenet\_2022 proposed a point cloud completion network (Lake-net) for furniture model point cloud datasets.} 
For grape berry application, the shape of the berry can be roughly approached by the deformation of a sphere or ellipsoid depending on the species. 
Existing datasets from other fruits cannot be applied directly, and manually creating paired training datasets is time-consuming and labor-intensive.
Therefore, there is a demand to develop an analysis pipeline, capable of completing the detailed surface of an incomplete berry point cloud while requiring less labor-intensive training data preparation.

>>>>

% \textbf{\added{Highlights}}
% \begin{itemize}
% %   \item Novel deep learning pipeline for automated 3D grape phenotyping.
% %   \item GrapeCPNet: Self-supervised network for berry points cloud completion.
% %   \item High accuracy in berry instance segmentation (99.5\% average precision).
% %   \item Robust performance across four grape varieties ($R^2$ of 0.855 for radius, 0.969 for 
% % volume).
% %   \item Non-destructive and high-throughput analysis for viticulture applications.
%   \item \added{GrapeCPNet completes 3D point clouds for segmented berry instances.}
%   \item \added{GrapeCPNet is trained using self-supervision, free of manual annotations.}
%   \item \added{Integrated into a deep learning pipeline for automated 3D grape bunch phenotyping.}
%   \item \added{Achieved over 0.85 $R^2$ and 99.5\% average precision on four grape varieties.}
% \end{itemize}

@@

\added{Another challenge after the success of instance berry segmentation is the incomplete representation of berry surfaces.} 
The aggregated cluster growth causes the berries to squeezed against each other, leading to self occlusion and resulting in an incomplete point cloud of berry surfaces \citep{du_instance_2023}. 
Therefore, point cloud instance segmentation can only capture partial information rather than that of whole berries.
To address \replaced{this issue}{the issue of partial point clouds,} and consequently an underestimation of the berry traits, point cloud shape completion is one of the most commonly used solutions.
Point cloud completion is the task of generating a complete 3D shape given partial point cloud input \citep{tesema_point_2024}. 
For instance, \citet{ge_symmetrybased_2020} assume that strawberries are symmetrical, suggesting that their shape can be completed by , provided an appropriate symmetrical plane can be identified.
\citet{marangoz_fruit_2022} proposed an super-ellipsoids matching approach to map fruits on plants and estimate their shape.
However, these methods are limited to specific fruit characteristics and require manual design of algorithms according to the features of the fruit, lacking the potential for generalized application.
Utilizing deep learning methods, researchers have designed point cloud completion networks \citep{wang_unsupervised_2021}. 
\citet{park_deepsdf_2019} introduced DeepSDF to achieve the completion of object point cloud models. It uses a learned continuous signed distance function to represent a class of shapes in latent space and is tolerant to noisy 3D input data. 
\citet{magistri_contrastive_2022} utilized DeepSDF and its latent space in an encoder-decoder network that converted a single RGB-D frame to a 3D shape of a complete fruit. 
This encoder-decoder network was extended and optimized by \citet{blok_highthroughput_2025} for high-throughput 3D shape completion of potato tubers on a commercial harvester. 
\deleted{Outside the agricultural domain, tang\_lakenet\_2022 proposed a point cloud completion network (Lake-net) for furniture model point cloud datasets.} 
For grape berry application, the shape of the berry can be roughly approached by the deformation of a sphere or ellipsoid depending on the species. 
Existing datasets from other fruits cannot be applied directly, and manually creating paired training datasets is time-consuming and labor-intensive.
Therefore, there is a demand to develop an analysis pipeline, capable of completing the detailed surface of an incomplete berry point cloud while requiring less labor-intensive training data preparation.
